### 2015-05-30 writing/SNLI paper/abstract.tex
Incremental paper update.

\begin{abstract} 
Understanding entailment and contradiction is  fundamental to understanding natural language, and inference about entailment and contradiction is a valuable testing ground for the development of semantic representations. 
However, research in this area has been dramatically limited by the lack of large-scale resources. 
To address this, we introduce a new freely available corpus of labeled sentence pairs, written by humans in a novel grounded task framing based on image captioning. 
At 570K pairs, it is two orders of magnitude larger than all other resources of its type. 
In this paper, we use this corpus to evaluate a wide variety of natural language inference models, finding that Tree-Structured Long Short-Term Memory networks (TreeLSTMs) achieve the best performance. 
In addition, we show that models trained on our corpus perform competitively on an existing NLI test set.
\end{abstract}

>>>>

\begin{abstract} 
Understanding entailment and contradiction is  fundamental to understanding natural language, and inference about entailment and contradiction is a valuable testing ground for the development of semantic representations. 
However, research in this area has been dramatically limited by the lack of large-scale resources. 
To address this, we introduce a new freely available corpus of labeled sentence pairs, written by humans in a novel grounded task framing based on image captioning. 
At 570K pairs, it is two orders of magnitude larger than all other resources of its type. 
We also use this corpus to evaluate several natural language inference models. We find that a simple Long Short-Term Memory (LSTM) based model trained on our corpus not only performs competitively on our own evaluation set, but also achieves the best reported performance for a neural network model on an existing natural language inference benchmark.
\end{abstract}

### 2015-05-30 writing/SNLI paper/entailment_eval.tex
Incremental paper update.

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{Our corpus}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{67.9} & \t{38.7} & \t{49.3} & \t{7X.X} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
3-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
In order to calibrate the difficulty of the dataset against the 
  classical RTE problems, results are also reported on the (2-class) 
  RTE-3 dataset.
\todo{Cite RTE-3 here.}
\todo{Final numbers}
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{eopresults}.
The best edit distance algorithm tunes the weight of the three 
  case-insensitive edit distance operations on the training set, 
  after removing stop words.
The best classifier-based system makes use of information from
  WordNet \cite{miller1995wordnet} and VerbOcean
  \cite{chklovski2004verbocean}, and makes use of features
  based on tree patterns and dependency tree skeletons
  \cite{wang2007recognizing}.
Unsurprisingly, the classification-based approach outperforms simple
  edit distance metrics, and performs quite well despite relatively
  little lexicalization.

@@

% Commenting out until PDF available. -S
% Running 'make' should generate PDF from gnuplot
\Fig{learning_curves_bow.pdf}{0.45}{bowlearncurve}{
A learning curve for the lexicalized and unlexicalized baseline classifiers,
plotted on a log scale.
Note the y axis starting at a random-chance accuracy of 33\%.
}

% Results
We report results in \reftab{bowresults}, along with ablation studies for removing
  the bigram features (leaving only the unigram entailment pair feature),
  and for removing all lexicalized features.
In addition, we report learning curves for the lexicalized and fully unlexicalized
  classifiers in \reffig{bowlearncurve}.

% Insights 1: lexicalization helps a bunch
It is interesting to note the substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
In fact, the addition of these features alone allow the classifier to
  outperform the RTE baselines -- this is in some sense unsurprising:
  the RTE systems have been tuned on relatively small corpora
  ($\sim$1600 examples), whereas a classifier trained on our corpus can make use of
  over two orders of magnitude more data.
  \todo{Use curve to justify large size of corpus.}

% Insights 2: the learning curve for the unlexicalized classifier is sad
More surprising is how quickly the lexicalized classifier outperforms its
  unlexicalized counterpart (see \reffig{bowlearncurve}).
With only 100 training examples, the cross-bigram classifier is already
  outperforming its unlexicalized counterpart.
Empirically we notice that the top weighted features for the classifier
  trained on 100 examples tend to be high precision entailments;
  e.g.,
  \textit{playing} $\rightarrow$ \textit{outside}
  (most scenes are outdoors), or \textit{a banana} $\rightarrow$
  \textit{person eating}.
If relatively few spurious entailments get high weight -- as it appears
  is the case -- then it makes sense that when these do fire they
  provide some boost in accuracy.

%\subsection{Existing NLI systems}

@@

Our neural network classifier, depicted in Fig.~\ref{modelstructure} is simply a stack of three 100d $\tanh$ layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the representation model itself.

We test six sentence representation models, each set to use 50d word and phrase embeddings. Our baseline model in this experiment simply sums the embeddings of the word in each sentence. Next, we experiment with two recurrent models: a plain RNN, and a one-layer LSTM RNN \cite{hochreiter1997long}. Finally, we experiment with three tree-structured models: a plain TreeRNN \cite{socher2011semi}, a tensor-parameterized TreeRNTN \cite{socher2013acl1}, and a TreeLSTM \cite{tai2015improved}.

The word embeddings for all of the models are initialized with the 300d reference GloVe vectors (840B token version, \citealt{pennington2014glove}) and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensional phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{75?} & \t{72?} \\	
\t{100d LSTM RNN}            & \t{81.4?} & \t{78.2?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{61?} & \t{60?} \\
\t{100d LSTM TreeRNN}            & \t{72?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the our training and test sets for each model.
\todo{Replace with final numbers/dims}
}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d LSTM RNN (random init.)}            & \t{100} & \t{71.3} \\
% From: ~/quant/transfer-sick-only-l0.0001-dim50-ed200-td3-pen100-do0.9-0.9-ws1-par0-comp2-cdim1/
\t{100d LSTM RNN (transfer init.)}            & \t{100?} & \t{80?} \\
% From: 
\hline
\end{tabular}
\end{center}

@@

\todo{Why not RTE3?}

@@

>>>>

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{Our corpus}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{67.9} & \t{38.7} & \t{49.3} & \t{7X.X} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
3-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
In order to calibrate the difficulty of the dataset against the 
  classical RTE problems, results are also reported on the (2-class) 
  RTE-3 dataset.
\todo{Final numbers}
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{eopresults}, covering both our own test set 
and the standard RTE-3 test set \cite{giampiccolo2007third}.
The best edit distance algorithm tunes the weight of the three 
  case-insensitive edit distance operations on the training set, 
  after removing stop words.
The best classifier-based system makes use of information from
  WordNet \cite{miller1995wordnet} and VerbOcean
  \cite{chklovski2004verbocean}, and makes use of features
  based on tree patterns and dependency tree skeletons
  \cite{wang2007recognizing}.
Unsurprisingly, the classification-based approach outperforms simple
  edit distance metrics, and performs quite well despite relatively
  little lexicalization.
\todo{Is the RTE3 model trained on RTE3?}

@@

% Results
We report results in \reftab{bowresults}, along with ablation studies for removing
  the bigram features (leaving only the unigram entailment pair feature),
  and for removing all lexicalized features.

% Insights 1: lexicalization helps a bunch
It is interesting to note the substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
In fact, the addition of these features alone allow the classifier to
  outperform the EOP models -- this is in some sense unsurprising:
  the EOP systems have been tuned on relatively small corpora
  ($\sim$1600 examples), whereas a classifier trained on our corpus can make use of
  over two orders of magnitude more data.
  \todo{Use curve to justify large size of corpus.}

@@

Our neural network classifier, depicted in Fig.~\ref{modelstructure} is simply a stack of three 200d $\tanh$ layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the representation model itself.

We test three sentence representation models, each set to use 100d word and phrase embeddings. Our baseline model in this experiment simply sums the embeddings of the word in each sentence. In addition, we experiment with two simple sequence embedding models models: a plain RNN and an LSTM RNN \cite{hochreiter1997long}. Both use the simple conventional layout with one layer per input token.

The word embeddings for all of the models are initialized with the 300d reference GloVe vectors (840B token version, \citealt{pennington2014glove}) and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensional phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were implemented in a common framework for this paper, and the implementations will be made available at publication time.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{75?} & \t{72?} \\	
\t{100d LSTM RNN}            & \t{81.4?} & \t{78.0?} \\
% \t{100d TreeRNN}            & \t{69?} & \t{69?} \\
% \t{50d TreeRNTN}            & \t{61?} & \t{60?} \\
% \t{100d LSTM TreeRNN}            & \t{72?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on our training and test sets for each model.
\todo{Replace with final numbers/dims}
}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d LSTM RNN (random init.)}            & \t{100} & \t{71.3} \\
% From: ~/quant/transfer-sick-only-l0.0001-dim50-ed200-td3-pen100-do0.9-0.9-ws1-par0-comp2-cdim1/
\t{100d LSTM RNN (transfer init.)}            & \t{100?} & \t{80.4?} \\
% From: ...
\hline
\end{tabular}
\end{center}

@@

@@

We attempted to apply this same transfer evaluation technique to the RTE-3 challenge dataset, but found that the small size of the training set (800 examples) did not allow our model to adapt to the

\subsection{Further analysis}

Fig.~\reffig{bowlearncurve} shows a learning curve for the LSTM and the lexicalized and unlexicalized feature-based models. Here, we observe further confirmation that supervised neural network models like our LSTM-based model are only competitive 
% describe intersection
% promising with more data
% useful resource in the development of more sophisticated SE models

\Fig{learning_curves_bow.pdf}{0.45}{bowlearncurve}{
A learning curve for the lexicalized and unlexicalized baseline classifiers and the LSTM,
plotted on a log scale. The minibatch-based training method that we chose for the LSTM requires at least 64 examples to function. Note that the y axis starts at a random-chance accuracy of 33\%. \todo{One more LSTM data point at ~80}}

% Insights 2: the learning curve for the unlexicalized classifier is sad
Setting aside the neural network model, were surprised at how quickly
the lexicalized classifier outperforms its
  unlexicalized counterpart (see \reffig{bowlearncurve}).
With only 100 training examples, the cross-bigram classifier is already
  outperforming its unlexicalized counterpart.
Empirically we notice that the top weighted features for the classifier
  trained on 100 examples tend to be high precision entailments;
  e.g.,
  \textit{playing} $\rightarrow$ \textit{outside}
  (most scenes are outdoors), or \textit{a banana} $\rightarrow$
  \textit{person eating}.
If relatively few spurious entailments get high weight -- as it appears
  is the case -- then it makes sense that when these do fire they
  provide some boost in accuracy.

  \todo{Insert example-specific error analysis}

### 2015-05-30 writing/SNLI paper/intro.tex
Incremental paper update.

@@

In this paper, we use this corpus to evaluate a wide variety of models
for natural language inference, including rule-based systems, simple
linear classifiers, and compositional neural networks. We find that
Tree-Structured Long Short-Term Memory networks (TreeLSTMs;
\citealt{tai2015improved,le2015compositional}) achieve the best
performance. In addition, we enhance the case for TreeLSTMs by showing
that its representations, trained on our corpus, perform well in a
disparate set of additional semantic tasks.  The success of these
transfer-learning experiments is also a testament to the centrality
of NLI in semantics.

\todo{TreeLSTM vs. LSTM result TBD.}

>>>>

\begin{table*}[t]
  \centering\footnotesize
  \begin{tabular}{p{6cm}p{0.75cm}p{1.4cm}p{6cm}}
  \toprule
A man inspects the uniform of a figure in some East Asian country. & \b{contr.}& \t{$\{$c c c c c$\}$} & The man is sleeping\\
\rule{0pt}{3ex}An older and younger man smiling. & \b{neut.}& \t{$\{$n n e n n$\}$} & Two men are smiling and laughing at the cats playing on the floor.\\
\rule{0pt}{3ex}A black race car starts up in front of a crowd of people. & \b{contr.}& \t{$\{$c c c c c$\}$} & A man is driving down a lonely road.\\
\rule{0pt}{3ex}A soccer game with multiple males playing. & \b{ent.}& \t{$\{$e e e e e$\}$} & Some men are playing a sport.\\
\rule{0pt}{3ex}A smiling costumed woman is holding an umbrella. & \b{neut.}& \t{$\{$n n e c n$\}$} & A happy woman in a fairy costume holds an umbrella.\\
    \bottomrule
% From 1.0rc3
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from the development section of our new corpus, shown with both the gold labels and the full set of annotator labels (abbreviated).}
\end{table*}

@@

In this paper, we use this corpus to evaluate a wide variety of models
for natural language inference, including rule-based systems, simple
linear classifiers, and compositional neural networks. We find that
a neural network model based on a Long Short-Term Memory network (LSTM; 
\citealt{hochreiter1997long}) for sentence embedding achieves the best
performance, and we validate that strong performance by showing that
a model trained on our data can be successfully adapted to an existing
NLI challenge task, yielding the best reported performance for a neural network model.
